---
title: ""
output: github_document
---

```{r, eval=T, echo=F}
source('../inst/forelesningsnotater/timeplan.R')
```

Forelesning #1: [`r tema[1]`](https://github.com/joernih/SFB10816Mikrooekonomi/blob/main/inst/forelesningsnotater/1-3_introduksjon.pdf)

## Produsentteori: Produsentens økonomiske adferd

Forelesning #2: [`r tema[2]`](https://github.com/joernih/BOEA203Mikrooekonomi/blob/main/inst/pdfs/4%20Produksjonsteori:Produksjon.pdf)
<br>
Forelesning #3: [`r tema[3]`](https://github.com/joernih/BOEA203Mikrooekonomi/blob/main/inst/pdfs/5%20Produksjonsteori:Inntekter_og_kostnader.pdf)
<br>
Forelesning #4: [`r tema[4]`](https://github.com/joernih/BOEA203Mikrooekonomi/blob/main/inst/pdfs/6_Produsentteori:Produkt_og_faktormarkeder.pdf)

## Konsumentteori: Konsumentens økonomiske adferd

Forelesning #5: [`r tema[5]`](https://github.com/joernih/BOEA203Mikrooekonomi/blob/main/inst/pdfs/7_Konsumentens_tilpasning.pdf)
<br>
Forelesning #6: [`r tema[6]`](https://github.com/joernih/BOEA203Mikrooekonomi/blob/main/inst/pdfs/8_Konsumentens_adferd.pdf)

```{r echo=F}
knitr::knit_exit()
```
## Markedsteori

Forelesning #7: [`r tema[7]`](https://github.com/joernih/SFB10816Mikrooekonomi/blob/main/inst/forelesningsnotater/9_markedsform_fullkommen.pdf)
<br>
Forelesning #8: [`r tema[8]`](https://github.com/joernih/SFB10816Mikrooekonomi/blob/main/inst/forelesningsnotater/10_markedsform_monopol.pdf)
<br>
Forelesning #9: [`r tema[9]`](https://github.com/joernih/SFB10816Mikrooekonomi/blob/main/inst/forelesningsnotater/11_markedsform_ufullkommen.pdf)
<br>
Forelesning #10: [`r tema[10]`](https://github.com/joernih/SFB10816Mikrooekonomi/blob/main/inst/forelesningsnotater/12_prisdiskriminering.pdf)

## Andre Emner

Forelesning #11: [`r tema[11]`](https://github.com/joernih/SFB10816Mikrooekonomi/blob/main/inst/forelesningsnotater/13_effektivitet_markedssvikt.pdf)
<br>
Forelesning #12: [`r substring(tema[12],1,15)`](https://github.com/joernih/SFB10816Mikrooekonomi/blob/main/inst/forelesningsnotater/14_litt_spillteori.pdf)`r substring(tema[12],17,nchar(tema[12]))`
<br>
Forelesning #13: `r tema[13]`

```{r echo=F}
knitr::knit_exit()
```

